System Model\vspace{-.1cm}

### 2021-03-04 NetworkSlicing/report_ns/report.tex

\title{Joint Power Allocation and Network Slicing in an Open RAN System \vspace{-.1cm}
}
%
%\author{\IEEEauthorblockN{1\textsuperscript{st} Mojdeh Karbalaee Motalleb}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%mojdeh.karbalaee@ut.ac.ir}
%\and
%\IEEEauthorblockN{2\textsuperscript{nd} Vahid Shah-Mansouri}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%vmansouri@ut.ac.ir}
%\and
%\IEEEauthorblockN{3\textsuperscript{rd} Salar Nouri Naghadeh}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%salar.nouri@ut.ac.ir}
%}
  \author{
    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb, Vahid Shah-Mansouri, Salar Nouri Naghadeh}
    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
    Email: \{mojdeh.karbalaee, vmansouri, salar.nouri\}@ut.ac.ir,
    \vspace{-.2cm}
  }
  }

@@

\begin{abstract}
Open radio access network (ORAN) alliance which has been formed recently establishes a flexible,  open, and smart radio access network (RAN) by combing the ideas from xRAN and cloud RAN (C-RAN). ORAN divides the functions of the RAN into three parts, namely remote unit (RU), distributed unit (DU), and central unit (CU). While RU contains lower PHY functions, DU contains higher PHY, MAC, and RLC and CU contains RRC, PDCP, and SDAP. CU and DU are implemented as virtual network functions (VNFs) running on a cloud environment. Interfaces between RU, CU, and DU are open standard interfaces. Network slicing as a new concept in 5G systems is used to share the network resources between various services while the operation of one service does not affect another service. In this paper, we study the problem of RAN network slicing in an ORAN system.  We formulate the problem of wireless link scheduling, assigning the slices to the services, and assigning the physical data centers resource to slices which is 3D-bin packing problems. The objective is to jointly maximize the energy efficiency and minimize power consumption of RUs and the cost of physical resources in a downlink channel. The problem is formulated as a mixed-integer optimization problem that can be decomposed into two independent sub-problems. Heuristic algorithms are proposed for each of the sub-problems.
\end{abstract}

\begin{IEEEkeywords}
Open RAN (ORAN), network slicing, energy efficiency.
\end{IEEEkeywords}

\section{Introduction}
Open RAN (ORAN), as the integration and expansion of C-RAN and xRAN, is expected to be a key technology in 5G networks to extensively enhance the RAN performance. The core idea of C-RAN is to split the radio remote head (RRU) from the baseband unit (BBU). Several BBUs operating on a cloud server will create a BBU-Pool, providing unified baseband signal processing with powerful computing capabilities \cite{cran1,frdl,simeone2016cloud,motalleb2017optimal}. On the other hand, xRAN technology has three fundamental features. The control plane is decoupled from user plane. Besides, a modular eNB software stack is built to operate on common-off-the-shelf (COTS) hardware. Moreover, open north-bound and south-bound interfaces are introduced \cite{xran}.

ORAN virtualizes the elements of the radio access networks, separates them and defines appropriate open interfaces for connection of these elements. Moreover, ORAN uses machine learning techniques to develop smarter RAN layers in its architecture. In an innovative ORAN system, the programmable RAN software is decoupled from hardware \cite{oran1}. Open interface is one of the most crucial properties for ORAN to enable mobile network operators (MNOs) to define their own services.
The concept of software defined network (SDN), which is the separation of control plane from user plane, is deployed in an intelligent ORAN architecture. Moreover, this separation promotes RRM to use non-realtime (RT) and near-realtime (NRT) RAN Intelligent Controller (RIC).
In the ORAN architecture, distributed unit (DU) is a logical node having RLC/MAC/High-PHY layer.
Moreover, central unit (CU) is a logical node having RRC, SDAP and PDCP. Also, radio unit (RU) is a logical node having LOW-PHY layer and
RF processing \cite{oranpaper}.
ORAN introduces interfaces such as open fronthaul interface that connects DU and RU (i.e., E2 interface), and an A1 interface between orchestration/NMS layer containing the non-real-time RIC (RIC non-RT) function and the eNB/gNB containing the near-real-time RIC (RIC near-RT) function.

To evolve servicing in 5G networks, separation of elements of software and hardware of network is employed and referred to as network functions virtualization (NFV). Virtual network functions (VNFs) are functional blocks of the system. 5G networks are expected to host several services with different requirements simultaneously. Network slicing is considered as a solution for such demand. A network slice is a logical end-to-end network which provides service with specific requirements. Multiple network slices run on the same network infrastructure which are managed and operated independently \cite{lee2018dynamic}. Slicing can be defined for the RAN, for the core network or both of them \cite{ns1}.

Based on their type of service request, user equipments (UEs) are classified into various services, where UEs in the same service have similar service requests. In addition, each service is mapped to one or more slices based on the resources of the slices. Each VNF of the ORAN is mapped to one or more virtual machines (VMs) in the data center. For simplicity of analysis and without loss of generality, we assume a VNF is mapped to one VM and requires specific physical resources including storage, memory, and processing \cite{frdl,luong2018novel,luong2018novel1}.

%The compression of messages passed through the fronthaul link due to the limited capacity of these links is considered in \cite{simeone2016cloud,1111}.
In \cite{oranT},  the evolution of RAN in the  5G network is described. The architecture of C-RAN and xRAN is expressed and development of the ORAN from C-RAN and xRAN is explained. Also requirements of the network in terms of capacity and latency is taken into account.
In \cite{oran12},  the ORAN architecture is studied. The eight working groups are discussed including: focus areas of ORAN alliance which contains use-cases, overall architecture,  open interfaces, and  the virtualization and modularization of hardware and software. To the best of our knowledge, there is not work in the literature to model ORAN systems.

%We shortly review related works in the area of C-RAN and xRAN. In \cite{motalleb2017optimal}, power allocation in C-RAN architecture, with limited fronthaul capacity in clustered network is studied. In \cite{lee2018dynamic}, dynamic network slicing is considered in heterogeneous CRAN (H-CRAN) to maximize the weighted sum-rate. Also, two level network slicing (upper and lower level) is done. The admission of UEs is maximized using the heuristic algorithms. In addition, the allocation of BBU capacity to UEs is considered. In \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting} minimization of cost obtained by power consumption, also cloud processing and limited power for each RU is considered. Furthermore, the processing delay of each VM and wireless transmission delay are taken into account. In \cite{frdl}, the processing and transmission delay is modeled as a M/M/1 queue. In \cite{guo2016exploiting}, M/D/1 queue is used to modeled the transmission delay.

\begin{figure}
  \centering
    \includegraphics[scale=0.55]{c7.pdf}
  \caption{Network sliced ORAN system}
  \label{fig:c11}
\end{figure}

In this paper, as  depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied. The RAN is divided into three layers including RU, DU, and CU with open interfaces. DU and CU are running on general purpose data centers. UEs are divided to different services according to their requirements. RAN resources are partitioned into slices to provide requirements of services. Optimal power allocation and joint mapping of slices to services are applied. In addition, mapping slices to physical resources is taken into account. The contributions of the paper are as follows:
\begin{itemize}
\item Joint network slicing and resource allocation is considered in an ORAN system.
\item We formulate the problem of assigning UEs to services, services to slices, and physical wireless and data center resources to the slices as an optimization problem.
\item Novel heuristic algorithms are applied for these sub-problems to efficiently obtain the solution.
\end{itemize}

The rest of the paper is organized as follows. In Section \ref{systemmodel}, system model which contains obtaining achievable rates, processing and transmission delay, and physical data center resources is introduced. Then, problem statement is explained and decomposed into two independent sub-problems.
In Section \ref{proposedmethod}, heuristic algorithms for the sub-problems is presented. In Section \ref{simul}, numerical results are provided to investigate the performance of the algorithms.

\section{System Model and Problem Formulation}\label{systemmodel}

@@

single-antenna UEs that require certain service. Each slice $s \in \{1,2,...,S \}$ consists of $R_s$ RUs and $K_s$ physical resource blocks (PRBs), one DU and one CU that contains VNFs.
Slices can have shared resources. All RUs in a slice, that are mapped to a service, transmit signals cooperatively to all the UEs in a specific service \cite{motalleb2017optimal,mimoCran}. Each RU $r \in \{1,2,...,R \}$ is mapped to a DU via an optical fiber link with limited fronthaul capacity.

@@

\mathcal{R}_{u(v,i)} = B \log_2({1+ \rho_{u(v,i)}}),

@@

where $B$ is the bandwidth of system and $\rho_{u(v,i)}$ is the SNR of $i^{th}$ UE in $v^{th}$ service which is obtained from

@@

\rho_{u(v,i)} =  \frac{p_{u(v,i)}\sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{v,s}}{BN_0 + I_{u(v,i)}},

@@

where $p_{u(v,i)}$ represents the transmission power allocated by RUs to $i^{th}$ UE in $v^{th}$ service, and
$\bold{h}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ is the vector of channel gain of a wireless link from RUs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service. In addition, $\bold{w}_{R_s,u(v,i)} \in \mathbb{C}^{{R}_s}$ depicts the  transmit beamforming vector from RUs in the $s^{th}$ slice to the $i^{th}$ UE in $v^{th}$ service. Moreover, $BN_0$ denotes the power of Gaussian additive noise, and $I_{u(v,i)}$ is the power of interfering signals. Moreover, $a_{v,s} \in \{0,1\}$ is a binary variable that illustrates whether slice $s$ is mapped to service $v$ or not. If $a_{v,s} =1$ then, $v^{th}$ service is mapped to $s^{th}$ slice; otherwise, it is not mapped.

@@

\textstyle \bold{y}_{U_v} = \sum_{s = 1}^{S}\sum_{k=1}^{K_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v} \
\mathfrak{y}_{R_s}\zeta_{U_v,k,s} a_{v,s}+ \boldsymbol{z}_{\mathcal{U}_v},

@@

where $\mathfrak{y}_{R_s} = \boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{U}_v}+ \boldsymbol{q}_{\mathcal{R}_s}$

@@

In addition, $\boldsymbol{q}_{R_s} \in \mathbb{C}^{{R}_s }  $ indicates the quantization noise, which is made from signal compression in DU.

@@

Furthermore, $\zeta_{k,s}^{U_v} \delequal \{\zeta_{k,s}^{u(v,1)},\zeta_{k,s}^{u(v,2)},...,\zeta_{k,s}^{u(v,N_{U_v})}\}$,
$\zeta_{k,s}^{u(v,i)} \in \{0,1\}$ is a binary parameter, which demonstrates whether $i^{th}$ UE in $v^{th}$ service can transmit its signals through $k^{th}$ PRB and also this PRB belongs to $s^{th}$ slice or not.
$\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}=\left[\boldsymbol{h}_{\mathcal{R}_s,u_{(v,1)}},\ldots,\boldsymbol{h}_{\mathcal{R}_s,v_{(v,\mathcal{U}_v)}}\right]^T  \in \mathbb{C}^{{R}_s\times {U}_v }$
shows the channel matrix between RU set $\mathcal{R}_s$ to UE set

@@

Moreover, $\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = [\boldsymbol{w}_{\mathcal{R}_s,u(v,1)},...,\boldsymbol{w}_{\mathcal{R}_s,u(v,U_v)}] \in \mathbb{C}^{{R}_s\times U_v} $ is the zero forcing beamforming vector to minimize the interference which is indicated as below

@@

\textstyle \boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v} = \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v}^H \boldsymbol{H}_{\mathcal{R}_s,\mathcal{U}_v})^{-1}.

@@

 \underbrace{\sum_{s=1}^{S}\sum_{n=1}^{S}\sum_{\substack{l=1 \\ l\neq i}}^{{U}_v} \gamma_{1}  p_{u_{(v,l)}}a_{v,s}\zeta_{u_(v,i),n,s}\zeta_{u_(v,l),n,s}}_{\text{(intra-service interference)}}\\
&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{s=1}^{S}\sum_{n=1}^{S}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u_{(y,l)}}a_{y,s} \zeta_{u_(v,i),n,s}\zeta_{u_(y,l),n,s}}_{\text{(inter-service interference)}}\\
&+\underbrace{ \sum_{s=1}^{S} \sum_{j=1}^{{R}_s} {\sigma_q}_{r_{(s,j)}}^2 |\boldsymbol{h}_{r_{(s,j)}, u_{(v,i)}}|^2 a_{v,s}}_{\text{(quantization noise interference)}},

@@

where $\gamma_{1} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(v,l)}}|^2$
and $\gamma_{2} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(y,l)}}|^2$. Moreover,

@@

\bar{p}_{r_{(s,j)}} = \sum_{v=1}^{V}\boldsymbol{w}_{r_{(s,j)},\mathcal{U}_{v}} \boldsymbol{P}_{\mathcal{U}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{U}_v}^{H \frac{1}{2}}   \boldsymbol{w}_{r_{(s,j)},\mathcal{U}_{v}}^H a_{v,s} + \sigma_{q_{r(s,j)}}^2.

@@

Nevertheless, the rate of users on the fronthual link between DU and the $j^{th}$ RU in $s^{th}$ slice is formulated as \cite{simeone2016cloud, 1111}

@@

 an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue \cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}. Therefore,

@@

\section{Heuristic Method}\label{proposedmethod}
In this subsection, a heuristic  method is proposed to solve the problem in \eqref{constraints1} which is non-convex and computationally hard. To make it tractable, we divide the problem \eqref{constraints1} into
two different part that can be solved iteratively.
In the first part of sub-problem 1, we obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P} = P_{max}$ in \eqref{constraints1}. Also, we set $\eta = 0$. Afterward, by achieving $\boldsymbol{A}$, in the second part, we find $\boldsymbol{P}$ by using \eqref{constraints1}. This part of the sub-problem can be approximated and converted to a convex problem, so the sub-problem can be solved by convex methods. After solving $\boldsymbol{P}$, $\eta$ is updated. Then in the next iteration, with new $\boldsymbol{P}$
and $\eta$, the two parts of the sub-problems are solved. We repeat this procedure until the algorithm  converges.
\subsection{First Part of Sub-Problem 1}\label{firstsub}
Iterative algorithms are applied to acquire $\boldsymbol{A}$.
Since the first part of sub-problem is 3D-bin packing problem which is NP-hard, we need heuristic algorithm. In \cite{3dbin}, a heuristic algorithm is defined based on sorting bins according to a measurement.
The details of the heuristic algorithm are represented in algorithm \ref{alg}\cite{3dbin}.
\begin{algorithm}
\caption{Mapping Slice to Service}\label{alg}
\begin{algorithmic}[1]
\State Sort services according to the number of UEs in it and their requirements in the descending order.
\State Sort slices according to the weighted linear combination of number of PRBs, RUs and VNFs in two layers and the capacity of their resources in the descending order.
\For {$i \gets 1$ to $S$}
\For {$j \gets 1$ to $V$}
\State Set $a_{i,j} = 1$
\State Obtain Parameters of Systems (power and rate of UEs, rate of fronhaul links, power of RUs)
\If {conditions \eqref{c11}, \eqref{c12}, \eqref{c13} and \eqref{c14} are not applied}
\State Set $a_{i,j} = 0$;
\Else
\State break from inner loop;
\EndIf
\State \textbf{end if}
\EndFor
\State \textbf{end for}
\EndFor
\State \textbf{end for}
\end{algorithmic}
\end{algorithm}
\subsection{Second Part of Sub-Problem 1}\label{secondsub}
In this part, by assuming that $\boldsymbol{A}$ is fixed, the power of UEs in each service is achieved.
\begin{theorem}\label{t2}
The optimum energy efficiency is achieved if
\begin{equation}\label{q2}
%\begin{split}
\max \limits_{\boldsymbol{P}} (\mathfrak{R}_{tot}(\boldsymbol{P}) - \eta^* P_{r_{tot}}(\boldsymbol{P}))=
 \mathfrak{R}_{tot}(\boldsymbol{P}^*) - \eta^* P_{r_{tot}}(\boldsymbol{P}^*) =0.
%\end{split}
\end{theorem}
\begin{proof}
See \cite[Appendix A]{aaa}
\end{proof}
The second sub-problem can  be solved using the Lagrangian function and iterative algorithm.
Since, Interference is a function of the power of UEs, to make it tractable, we assume an upper bound $\bar{I}_{u_{(v,i)}}$ for interference. In order to make \eqref{constraints1} as a standard form of a convex optimization problem, it is required to change the variable of equations \eqref{cc14} and \eqref{cc15} ($p_{r_{(s,i)}} = \sigma_{q_{r(s,j)}}^2\times 2^{C_{r_{(s,i)}}}$ and $1/(D_{s}- d_{s_1} + d_{s_2})+\alpha_s$ respectively).
Assume $\boldsymbol{\lambda}$, $\boldsymbol{\mu}$, $\boldsymbol{\xi}$, and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.
The Lagrangian function is written as follow
\begin{subequations}\label{lagrang}
\mathcal{L}(\boldsymbol{P}; \boldsymbol{\lambda}, \boldsymbol{\chi}, \boldsymbol{\mu}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}) & = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v}\mathcal{\bar{R}}_{u_{(v,k)}}
- \eta \sum\limits_{v=1}^{V} \sum\limits_{i=1}^{\mathcal{R}_s}\bar{p}_{r_{(s,i)}}\\
&+\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \lambda_{u_{(v,k)}} (\mathcal{\bar{R}}_{u_{(v,k)}}-\mathcal{R}_{u_{(v,k)}}^{max})\\
&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \mu_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-P_{max})\\
&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \xi_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-\sigma_{q_{r(s,i)}}^2 2^{C_{r_{(s,i)}}^{max}}).\\
&+ \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \kappa_{u_{(v,k)}} \sum\limits_{s=1}^{S}(R_{u_{(v,k)}} -\mathfrak{D_s})a_{v,s}.
where, $\mathfrak{D_s}=\frac{1}{D_{s}^{max}-d_{s_1}-d_{s_2}}+\alpha_s$. Optimal power is obtained from  \eqref{lagrang}
p_{u(v,i)}^{*} = [\frac{\mathfrak{y}_{u(v,i)}\mathfrak{w}_{u(v,i)}-\mathfrak{x}_{u(v,i)}\mathfrak{z}_{u(v,i)}}{\mathfrak{x}_{u(v,i)}\mathfrak{w}_{u(v,i)} }]^+
where, $\mathfrak{y}_{u(v,i)}= (\lambda_{u(v,i)}+\kappa_{u_{(v,k)}}+1)\frac{B}{Ln_2}$ and
$\mathfrak{w}_{u(v,i)} = \sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{v,s}$. Also
$\mathfrak{z}_{u(v,i)} = BN_0 + \bar{I}_{u(v,i)}$ and $\mathfrak{x}_{u(v,i)} = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} ( \mu_{r_{u(s,i)}} + \xi_{r_{(s,i)}}+\eta)||w_{r_{(s,j)},u_{(v,i)}}||^2$.
By using sub-gradient method, the optimal power $\boldsymbol{P}$ is obtained \cite{mimoCran}.
%\section*{References}
\subsection{Solving two part of Sub-problem 1 iteratively}
In \eqref{firstsub} and \eqref{secondsub}, the details of solving each part of the sub-problem are depicted.
Firstly, we obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P} = P_{max}$ in the problem \eqref{constraints1} and using algorithm \eqref{alg}. Also we fixed $\eta = 0$. Afterward, $\boldsymbol{A}$ is achieved from algorithm \ref{alg}. Then, in the second part, we acquire $\boldsymbol{P}$ using the sub-gradient method. After solving $\boldsymbol{P}$, $\eta$ is updated. Then in the next iteration, with new $\boldsymbol{P}$
and $\eta$ the two parts of the sub-problem is solved until the algorithm converges.
Here, the algorithm of solving sub-problem 1 is shown in algorithm \eqref{alg2}
\begin{algorithm}
\caption{Joint Network Slicing and Power Allocation}\label{alg2}
\begin{algorithmic}[1]
\State Set the maximum number of iterations $I_{max}$, convergence condition $\epsilon_{\eta}$  and the initial value $\eta^{(1)} = 0$
\State Set $\boldsymbol{P} = \boldsymbol{P}_{max}$
\For {$counter \gets 1$ to $I_{max}$}
\State Achieve $\boldsymbol{A}$ by applying Algorithm \eqref{alg}
\State Obtain $\boldsymbol{P}$ by using sub-gradient method which is mentioned in \eqref{secondsub}.
\If {$ \mathfrak{R}_{tot}(\boldsymbol{P}^{(i)},\boldsymbol{A}^{(i)}) - \eta^{(i)} P_{r_{tot}}(\boldsymbol{P}^{(i)},\boldsymbol{A}^{(i)}) < \epsilon_{\eta} $}
\State Set $\boldsymbol{P}^*= \boldsymbol{P}^{(i)} $, $\boldsymbol{A}^*= \boldsymbol{A}^{(i)} $   and  $ \eta^{*} =\eta^{(i)} $;
\State break;
\Else
\State $i= i+1$, Setting $\boldsymbol{P} = \boldsymbol{P}^{(i)}$ ;
\EndIf
\State \textbf{end if}
\EndFor
\State \textbf{end for}
\end{algorithmic}
\end{algorithm}
\subsection{Sub-Problem 2}
In this subsection, we would like to solve  \eqref{constraints2}, which is the placement of virtual resources to physical resources in order to minimize the cost function $\psi_{tot}$.
The investigate problem is 3D-bin packing problem which is NP-hard.
To achieve optimum $\boldsymbol{Y}$ heuristic algorithm for 3D-bin packing is applied. The details of the heuristic algorithm are written in algorithm \eqref{alg3}. In this algorithm, firstly, we sort slices and DCs according to their sum-weighted of their requirements (line \ref{31} and line \ref{32} of algorithm \ref{alg3}).
We define a weighted parameter for $\Omega_{\mathfrak{z},s}^{tot}$ and $\tau_j^\mathfrak{z}$ as follow
\begin{equation}\label{wt}
\hat{\Omega}_{s}^{tot} &= w_M \bar{\Omega}_{M,s}^{tot} + w_S \bar{\Omega}_{S,s}^{tot} + w_C \bar{\Omega}_{C,s}^{tot} \\
\hat{\tau}_j &= w_M \tau_{{j}}^M + w_S \tau_{{j}}^S + w_C \tau_{{j}}^C,
where, $\boldsymbol{w} = \{w_M, w_S, w_C\}$ is the weight of memory, storage and CPU\cite{3dbin}.
Secondly, we start mapping from the most needed slices to the DC with the most physical resources (from line \ref{33} to line \ref{34} of algorithm \ref{alg3}). After mapping DCs to slices, If a slice does not admit to a specific DC, it remains for the next placement. In the next placement the remaining slices, map to more than one DC according to their requirements. (from line \ref{35} to line \ref{36} of algorithm \ref{alg3}). At the end, if DC with the lowest physical resources is free and can be served the slices of a DC with the highest physical resource, the slices remapped to new DC with the lowest physical resource since it has the lowest power consumption (line \ref{37} of algorithm \ref{alg3})\cite{3dbin}.
\begin{algorithm}
\caption{Placement of Physical resources into Virtual resources}\label{alg3}
\begin{algorithmic}[1]
\State Sort Slices according to $\hat{\Omega}_{s}^{tot} , \forall s$ in descending order.\label{31}
\State Sort DCs according to $\hat{\tau}_j , \forall j$ in descending order. \label{32}
\State $\boldsymbol{Y} = \boldsymbol{0}$
\For {$d \gets 1$ to $D_c$}\label{33}
\For {$s \gets 1$ to $S$}
\If {$\sum_{d=1}^{D_c}y_{s,d}==0$ and $\bar{\Omega}_{\mathfrak{z}(s)}^{tot} \leq \tau_{\mathfrak{z}_j} \forall \mathfrak{z}, \forall s$  }
\State Set $y_{s,d} = 1$;
\State {$\tau_j^{\mathfrak{z}}$ $\gets$ {$\tau_j^{\mathfrak{z}} - \bar{\Omega}_{\mathfrak{z},s}^{tot}$}} $\mathfrak{z}\in \{M,S,C\}$
\EndIf
\State \textbf{end if}
\EndFor

>>>>

\title{System Model\vspace{-.1cm}
}
%
%\author{\IEEEauthorblockN{1\textsuperscript{st} Mojdeh Karbalaee Motalleb}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%mojdeh.karbalaee@ut.ac.ir}
%\and
%\IEEEauthorblockN{2\textsuperscript{nd} Vahid Shah-Mansouri}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%vmansouri@ut.ac.ir}
%\and
%\IEEEauthorblockN{3\textsuperscript{rd} Salar Nouri Naghadeh}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%salar.nouri@ut.ac.ir}
%}
  \author{
    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb}
    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
    Email: \{mojdeh.karbalaee\}@ut.ac.ir,
    \vspace{-.2cm}
  }
  }

@@

\begin{abstract}

\end{abstract}
\begin{IEEEkeywords}

\end{IEEEkeywords}
\section{System Model and Problem Formulation}\label{systemmodel}

@@

single-antenna UEs that require certain service. Each Service is one of the instance of 3 type service contains URLLC, eMBB, MIoT. Each slice $s \in \{1,2,...,S \}$ consists of  $K_s$ physical resource blocks (PRBs), one DU and one CU that contains VNFs and physical resources from Data Centers.
Slices can have shared resources. All RUs can serve any users based on their distance and can transmit signals cooperatively to all the UEs in a specific place. Each RU $r \in \{1,2,...,R \}$ is mapped to a DU via an optical fiber link with limited fronthaul capacity.

@@

\mathcal{R}_{u(v,i)} = \sum_{s} B_s \log_2({1+ \rho_{u(v,i)} b_{u(v,i)}}) a_{v,s},

@@

where $B_s$ is the bandwidth of slice, $b_{u(v,i)}$ is a binary number represent whether the $i^{th}$ user in service $v$ is admitted in system or no and $\rho_{u(v,i)}$ is the SNR of $i^{th}$ UE in $v^{th}$ service which is obtained from

@@

\rho_{u(v,i)} =  \frac{p_{u(v,i)}\sum_{j=1}^{J}|\bold{h}_{R_j,u(v,i)}^H \bold{w}_{R_j,u(v,i)}|^2 e_{j,u(v,i)}}{BN_0 + I_{u(v,i)}},

@@

where $p_{u(v,i)}$ represents the transmission power allocated by RUs to $i^{th}$ UE in $v^{th}$ service,
$e_{j,u(v,i)}$ is the association of RRH j to user i in $v^{th}$ service.
and
$\bold{h}_{R_j,u(v,i)} \in \mathbb{C}^{{R}_j}$ is the vector of channel gain of a wireless link from RU j to the $i^{th}$ UE in $v^{th}$ service. In addition, $\bold{w}_{R_j,u(v,i)} \in \mathbb{C}^{{R}_j}$ depicts the transmit beamforming vector from RU j to the $i^{th}$ UE in $v^{th}$ service. Moreover, $BN_0$ denotes the power of Gaussian additive noise, and $I_{u(v,i)}$ is the power of interfering signals. Moreover, $a_{v,s} \in \{0,1\}$ is a binary variable that illustrates whether slice $s$ is mapped to service $v$ or not. If $a_{v,s} =1$ then, $v^{th}$ service is mapped to $s^{th}$ slice; otherwise, it is not mapped.

@@

\textstyle \bold{y}_{U_v} = \sum_{j = 1}^{J}\sum_{s = 1}^{S}\sum_{k=1}^{K_s} \boldsymbol{H}^H_{\mathcal{R}_j,\mathcal{U}_v} \
\mathfrak{y}_{R_j}\zeta_{k,s}^{U_v,j} b_{U_v} a_{v,s}+ \boldsymbol{z}_{\mathcal{U}_v},

@@

where $\mathfrak{y}_{R_j} = \boldsymbol{W}_{\mathcal{R}_j,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{U}_v}+ \boldsymbol{q}_{\mathcal{R}_j}$

@@

In addition, $\boldsymbol{q}_{R_j} \in \mathbb{C}^{{R}_j }  $ indicates the quantization noise, which is made from signal compression in DU.

@@

Furthermore, $\zeta_{k,s}^{U_v,j} \delequal \{\zeta_{k,s}^{u(v,1)},\zeta_{k,s}^{u(v,2)},...,\zeta_{k,s}^{u(v,N_{U_v})}\}$,
$\zeta_{k,s}^{u(v,i),j} \in \{0,1\}$ is a binary parameter, which demonstrates whether $i^{th}$ UE in $v^{th}$ service can transmit its signals through $j^{th}$ RU using $k^{th}$ PRB and also this PRB belongs to $s^{th}$ slice or not.
$\boldsymbol{H}_{\mathcal{R}_j,\mathcal{U}_v}=\left[\boldsymbol{h}_{\mathcal{R}_j,u_{(v,1)}},\ldots,\boldsymbol{h}_{\mathcal{R}_j,v_{(v,\mathcal{U}_v)}}\right]^T  \in \mathbb{C}^{{R}_j\times {U}_v }$
shows the channel matrix between RU set $\mathcal{R}_j$ to UE set

@@

Moreover, $\boldsymbol{W}_{\mathcal{R}_j,\mathcal{U}_v} = [\boldsymbol{w}_{\mathcal{R}_j,u(v,1)},...,\boldsymbol{w}_{\mathcal{R}_j,u(v,U_v)}] \in \mathbb{C}^{{R}_j\times U_v} $ is the zero forcing beamforming vector to minimize the interference which is indicated as below

@@

\textstyle \boldsymbol{W}_{\mathcal{R}_j,\mathcal{U}_v} = \boldsymbol{H}_{\mathcal{R}_j,\mathcal{U}_v}(\boldsymbol{H}_{\mathcal{R}_j,\mathcal{U}_v}^H \boldsymbol{H}_{\mathcal{R}_j,\mathcal{U}_v})^{-1}.

@@

 \underbrace{\sum_{s=1}^{S}\sum_{n=1}^{S}\sum_{j=1}^{J}\sum_{\hat{j}=1}^{J}\sum_{\substack{l=1 \\ l\neq i}}^{{U}_v} \gamma_{1}  p_{u_{(v,l)}}e_{j,u(v,i)}e_{\hat{j},u(v,l)}b_{u(v,i)}b_{u(v,l)}}_{\text{(intra-service interference)}}\\
&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{s=1}^{S}\sum_{n=1}^{S}\sum_{j=1}^{J}\sum_{\hat{j}=1}^{J}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u_{(y,l)}}e_{j,u(v,i)}e_{\hat{j},u(v,l)}b_{u(v,i)}b_{u(y,l)}}_{\text{(inter-service interference)}}\\
&+\underbrace{ \sum_{s=1}^{S} \sum_{j=1}^{J} {\sigma_q}_{R_j}^2 |\boldsymbol{h}_{R_j}, u_{(v,i)}|^2 a_{v,s} e_{j,u(v,i)}b_{u(v,i)}}_{\text{(quantization noise interference)}},

@@

where $\gamma_{1} =|\boldsymbol{h}_{\mathcal{R}_j, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{j},u_{(v,l)}}|^2 a_{v,s}\zeta_{n,s}^{u_(v,i),j}\zeta_{n,s}^{u_(v,l),\hat{j}}$
and $\gamma_{2} =|\boldsymbol{h}_{\mathcal{R}_j, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{j},u_{(y,l)}}|^2a_{y,s} \zeta_{n,s}^{u_(v,i),j}\zeta_{n,s}^{u_(y,l),\hat{j}}a_{v,s}$. Moreover,

@@

\bar{p}_{R_j} = \sum_{v=1}^{V}\boldsymbol{w}_{R_j,\mathcal{U}_{v}} \boldsymbol{P}_{\mathcal{U}_v}^{\frac{1}{2}} \boldsymbol{P}_{\mathcal{U}_v}^{H \frac{1}{2}}   \boldsymbol{w}_{r_{(s,j)},\mathcal{U}_{v}}^H a_{v,s} + \sigma_{q_{r(s,j)}}^2.

@@

Nevertheless, the rate of users on the fronthual link between DU and the $j^{th}$ RU in $s^{th}$ slice is formulated as 

@@

 an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue. Therefore,

@@

\bibliographystyle{IEEEtran}
\bibliography{references}
\end{document}
